\documentclass[a4paper,12pt]{article}

\input{../../docs/base_changelog}

\begin{document}

\changelogDoc{
    \unreleasedNewVersion{
        \changed {
            \item Default for condition check threshold interval, back to 1 second.
        }

        \fixed {
            \item Keybind toggle to turn mod on/off not saving things on toggle switch.
            \item Wonky stamina priority food selection.
        }
    }

    \newVersion{0.4.1}{}{
        \added {
            \item Provide a minimal translated string for keybind HUD message.
        }

        \fixed {
            \item Properly use food ID instead of their qualified version (which may start with something like (O)91 for banana). Now, we use just number 91 to block from eating bananas,
            which doesn't contradict the given example in the config menu.
        }
    }

    \newVersion{0.4.0}{}{
        \added {
            \item Show HUD message when mod's is toggled on/off with the keybind while playing.
            \item Player condition interval check now has an option to check every 1/3 of a second. Set this to 0 to make this check occuring far more often.
        }

        \changed {
            \item Forbidden list to take (global) qualified item ids only, which I believe is much more accurate to represent item type. One of the site to browse the item ids can be found here - https://stardewids.com/.
        }

        \fixed { \item Cheapest food option priority. A silly typo broke this whole logic. My silly self has fixed and added a bit more code to prevent this from happening again. }
    }

    \newVersion{0.3.0}{}{
        \added{
            \item New feature to entirely skip eating animation (and the world pauses that comes with it) for you to eat food on the go, automatically. Configurable.
        }

        \fixed { \item Stay in the last facing direction option. I forgot to handle this internally.. }
    }

    \newVersion{0.2.1}{}{
        \fixed{\item Forbidden list name when spaces are in use.}
    }

    \newVersion{0.2.0}{}{
        \added {
            \item Option to select cheapest food to eat.
            \item Improve Generic Config Menu settings page with more usage explanations.
        }

        \fixed {
            \item Minor performance improvements.
            \item Forbidden list input now can deal with stray whitespaces and commas. Also the names doesn't have to be case-sensitive.
        }


        \removed {
            \item (Breaking): prioritized food input list and instead I made the active inventory row as the as the highest food prioritization for consuming (left to right, depending on your configured "eating priority" setting).
        }

    }

    \shortNewVersion{0.1.0}{}{
        \item Initial release.
    }
}

\end{document}