\documentclass[a4paper,12pt]{article}

\def\subprojectname{Selective Eating}
\def\subProjectNormalizedName{SelectiveEating}

\title{\subprojectname}
\def\projectVersion{0.4.3}
\def\modId{26831}

\input{../../docs/base}

\begin{document}

\tableofcontents

\subprojecttitle{\subprojectname}{
	A simple quality-of-life mod to make eating easier and automatic with configurable settings.
}

\subprojectfeatures{\projectVersion}{
	\item Automatically eat food when you lose some health or energy. You can configure this eating priority strategy in the menu to either prioritize replenishing the most health or energy as much as possible, the lowest priced food to save money, or turn this extra strategy off at any time.
	\item Entirely skip eating animation (and the world pauses that come with it) for you to eat food on the go, automatically. Configurable.
	\item Forbid certain food from being eaten. Configurable.
	\item Prioritize the food in your inventory's active row for eating.
	\item An option to stay in the same facing direction even after eating.
	\item Increase or decrease eating time intervals for role-playing/challenge or performance reasons.
	\item Options can be configured through the \href{https://www.nexusmods.com/stardewvalley/mods/5098}{Generic Config Menu} or \texttt{config.json} file within the \texttt{SelectiveEating} mod directory.
}

\subProjectCompatIssues{\modId}{
	Untested.
}{
	\item Fluent Eating
	\item Auto-eat (including the 1.6 updated version)
}{
	\item No known issue.
}{\subProjectNormalizedName}

\subProjectDependencies{}

\subsection{For users}
\subsubsection{Installing SelectiveEating}
\begin{enumerate}
	\item This mod requires SMAPI, so please, install that and other listed requirements first.
	\item Unzip the files into the \textbf{Stardew Valley/Mods/SelectiveEating} game folder.
	\item Make sure the \textbf{SelectiveEating.dll}, \textbf{CloudyCore.dll}, \textbf{FSharp.Core.dll},
	      and \textbf{manifest.json} files are inside \textbf{SelectiveEating} folder, not in \textbf{Mods} folder.
	\item Launch the game through SMAPI launcher.
\end{enumerate}

\subprojectBuildInstructions{\subProjectNormalizedName}

\begin{verbatim}
		git clone https://github.com/cloudyluna/StardewValleyMods
		cd SelectiveEating
		make release
\end{verbatim}


\subProjectAcknowledge{\modId}{\subProjectNormalizedName}

\subProjectLicenseNotice


\end{document}
