\documentclass[a4paper,12pt]{article}

\input{../../docs/base_changelog}

\begin{document}

\changelogDoc{
    \newVersion{1.0.0}{2024-09-05}{
        Major overhaul.
        \added {
            \item Crab pots in \href{https://stardewvalleywiki.com/The_Mines}{mines/underground caves/dungeons} (level 20, 60, 100) now can collect jellies
            and the only jelly they will catch is cave jelly.
            Farm cave and Witch's swamp \texttt{are not affected}.
            \item Jellies can be of different quality than normal.
            \item
        }

        \changed{
            \item \texttt{Breaking change:} Treat jellies catch or collect chance like any regular crab pot fish object (clam, mussel, crab, etc)
            instead of trash.
            \newline
            \newline
            As it seems some players are farming jellies items and uses extra skill perks mod to completely remove trash or increase other
            crab pot fish, catch rate later in the game, I find it probably makes more sense
            to convert jelly from a "trash" item into a crab pot fish one in the long term.
            \item Rebalanced global river and ocean jellies catch rate so they don't always completely overtake
            things like crabs or clams all the time as these items are rarer than trash items. This is made to
            accommodate the change made above.
        }

        \removed{
            \item The option to replace all the trash from configuration menu.
            \newline
            \newline
            Users should move to use other mods that will remove trash spawn chance instead as it is now considered
            a non-goal and won't be much of use for this project.
        }
    }

    \newVersion{0.3.0}{2024-09-04}{
        \added{
            \item Crab pots in cave farm and witch's swamp area now have much higher chance to collect cave jellies.
            \item 10\% more chance for crab pots in cave farm than witch's swamp to collect cave jellies.
        }
    }

    \newVersion{0.2.0}{2024-08-29}{
        \added{
            \item Option to replace all trash that will be collected by crab pots with jellies. Configurable with Generic Mod Config Menu.
            \item Option to enable or disable this mod with config menu.
        }
    }

    \shortNewVersion{0.1.0}{}{
        \item Initial release.
    }
}

\end{document}
