\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{graphicx}

\title{SelectiveEating}
\author{Cloudyluna}
\date{\today}

\begin{document}
	
	\section{SelectiveEating by Cloudyluna}
	
	A simple quality of life mod to make eating easier and automatic with configurable settings.
	
	\subsubsection{Features}
	
	\begin{itemize}
		\item Automatically eats food when you lost some health or energy. You can configure this eating priority strategy in the configure menu to either prioritizing on replenishing the most health or energy as much as possible, the lowest priced food to save money or simply turn this extra strategy off at any time.
		\item Entirely skip eating animation (and the world pauses that comes with it) for you to eat food on the go, automatically. Configurable.
		\item Forbid certain food from being eaten. Configurable.
		\item Prioritize the food in your inventory's active row for eating.
		\item An option to stay in the same facing direction even after eating.
		\item Increase or decrease eating time interval for role playing/challenge or performance reasons.
		\item Options can be configured through \href{https://www.nexusmods.com/stardewvalley/mods/5098}{Generic Config Menu mod} or \texttt{config.json} file within the mod directory.
	\end{itemize}
	
	
	\subsection{Building}
	
	\begin{quote}
		Attention: Make sure you already have set up \$\textit{GAME\_PATH} pointing to your Stardew Valley game folder first.
	\end{quote}

	If you cloned this project from the Github and have \texttt{nix} installed, run \texttt{nix develop} to load the development environment. Then run \texttt{make} or \texttt{dotnet build} to build the project.
	
	\begin{verbatim}
		# Example to build SelectiveEating for release
		git clone https://github.com/cloudyluna/StardewValleyMods
		cd SelectiveEating
		make release
	\end{verbatim}
	
	\subsection{URL link to the repository}
	\href{https://github.com/cloudyluna/StardewValleyMods/tree/main/SelectiveEating}{Github repository}
	
	\subsection{Thanks to}
	\begin{itemize}
		\item \href{https://github.com/Pathoschild/SMAPI}{SMAPI dev and contributors} for making Stardew Valley modding accessible.
		
		\item \href{https://www.nexusmods.com/stardewvalley/mods/5098}{Generic Config Menu dev and contributors} for making mod configuration through GUI, simple and easy.
	\end{itemize}
	
	\subsection{License}
	
	\begin{itemize}
		\item This project is licensed under the AGPL-3.0-or-later. See the \texttt{LICENSE} file for details.
		
		\item  The bundled FSharp.Core is licensed under the MIT license. See \texttt{sublicenses/FSharp.MIT} file for details.
	\end{itemize}
	
	
\end{document}